Black hole mass function and its evolution -- the first prediction for the Einstein Telescope

### 2020-02-20 projects/GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/bold_face/main_revised_bold.tex
Backup and clean house work

\newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
\newcommand{\blue}[1]{\textcolor{blue}{#1}} 
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

@@

\begin{abstract}
The knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe. We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BHMF and its evolution with redshift.  We perform the Monte Carlo simulation of the measurements of chirp signals from binary BH systems (BBH) that could be detected by ET, including the BH masses and their luminosity distances (\dl). We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$. Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests for three different sets of parameters and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$. Furthermore, assuming four sets of parameters, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ accurately at the uncertainty level of $\sim0.5$. Our numerical tests verify the reliability of our method; however, the uncertainty levels of the inferred parameters only applies for the assumed sets of the parameters which shouldn't be considered as a universal value for the general case.
}
\end{abstract}

@@

Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.  Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precison. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. 
In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities. Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}. Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift. In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET. We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.

@@

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector. Numerical predictions of BBH inspirals detectable by ET 
have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios\citep{Ola2013, Biesiada2014}}. More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog. The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study. We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.

@@

We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system \textbf{as specified below. First key parameter is the redshift $z_s$.}  We sample the \textbf{merging BBH systems} according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
where the intrinsic BBH merger rate $\dot{n}_{0}(z_{s})$ is the one predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}, $\tilde{r}(z_{s})$ is the dimensionless comoving distance to the source, and $E (z_s)$ is
the dimensionless expansion rate of the universe at redshift $z_s$. 
%Note that the cosmological model we adopted is comply with the one in \citet{Dominik13}.
%For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is %fixed
\textbf{sampled from a uniform distribution} 
between $[M_{min}, m_1]$. Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF. 
\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}). We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system. We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.

Concerning the BHMF we consider two scenarios. In the first scenario, the exponent $\alpha$ is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET. In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
% \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{The above form is not motivated by any physical model.}
This is actually the first order Taylor expansion in the scale factor $a(t)$ for any function.

@@

\textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform. 
\blue{We note the fact that LIGO detections usually infer the properties an asymmetry upper and lower limit with ${\it skewed}$ possibility distributions. Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density as used to simulate the measured value} is:
 \begin{equation} \label{equ_lognorm}
P(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
 \end{equation}
\blue{We set up the standard errors for ${\cal M}_0$, \dl, and \mone\ by taking results by \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories. Note that the assumed uncertainty level of these properties should only affect the uncertainty (i.e., precision) of the inferred parameters, which wouldn't affect the validity (i.e., accuracy) test of our method.
}

@@

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{Illustration of the mock GW catalog} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
... & $...$ & ... & ... & ...\\
ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET. The reported values are the medians, with errors corresponding to the 16th and 84th percentiles.
}
\end{deluxetable}

@@

\subsection{Selection Effect}\label{sec_likelihood_sf}
The GW observations have a tendency to discover more significant events, known as Malmquist bias. \blue{For example, the} GW systems with higher values \mone\ \blue{trend to} produce stronger signals and thus have a higher probability to be detected. \blue{As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account}.

To overcome this selection effect, we introduce the selection factor $\eta$ for the GW event, which is the detecting probability of one event in a repeated simulation. 
The meaning of this factor $\eta$ is straightforward -- if one GW event has $\eta=0.2$, it means that this event has 80\% probability of being be missed. In other words, four equivalent events would have been missed. Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the possibility to its intrinsic value. Hence, to account for the selection effect, we calculate the likelihood as:}
 \begin{equation} \label{equ_lik_sf}
 P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
 \end{equation}
where $\eta$ is directly determined by the probability distribution of $\rho$, i.e. $\eta = P(\rho>8)$. In order to \blue{adopt the Equation~(\ref{SNR}) to derive the $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}. Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors; one can only take the \dl\ as redshift estimator.
\blue{Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal). Thus, the distribution of their product $\eta$ is also asymmetric. Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}. Note that in a Log-Normal distribution, the expected value are higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
We consider this skewness and recalibrate the inferred expected value of $1/\eta$ into the median value, in order to assign a non-biased $1/\eta$ to the calculation.
}

\begin{figure}%[!b]
\includegraphics[width=1.0\linewidth]{eta_distribution.pdf}
\caption{
\blue{
Assuming a set of \dl\ and \cmass\ as Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution. The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
}
}
\label{fig_eta}
\end{figure}

\subsection{Luminosity Distance as Redshift Estimator} 
\label{sec_dl_z}
%The redshift is not detectable by GW, however, can be inferred from the DL. 
In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$. The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.

>>>>

\newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
\newcommand{\blue}[1]{{\bf #1}} 
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

@@

\begin{abstract}
The knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe. We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BHMF and its evolution with redshift.  We perform the Monte Carlo simulation of the measurements of chirp signals from binary BH systems (BBH) that could be detected by ET, including the BH masses and their luminosity distances (\dl). We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$. Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$. Furthermore, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Taking a thousand of GW events and using \dl\ as the redshift estimator, our tests show that one could infer the value of evolving parameter $\alpha_1$ accurately with the uncertainty level of $\sim0.5$. Our numerical tests verify the reliability of our method. The uncertainty levels of the inferred parameters can be trusted directly for the several sets of the parameter we assumed, yet shouldn't be treated as a universal level for the general case.
}
\end{abstract}

@@

Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.  Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% {\bf precision}. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. 
In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities. Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}. Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift. In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET. We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.

@@

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector. Numerical predictions of BBH inspirals detectable by ET 
have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios \citep{Ola2013, Biesiada2014}}. More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog. The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study. We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.

@@

We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system \textbf{as specified below. First key parameter is the redshift $z_s$.}  We sample the \textbf{merging BBH systems} according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
where the intrinsic BBH merger rate $\dot{n}_{0}(z_{s})$ is the one predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}, $\tilde{r}(z_{s})$ is the dimensionless comoving distance to the source, and $E (z_s)$ is
the dimensionless expansion rate of the universe at redshift $z_s$. 
%Note that the cosmological model we adopted is comply with the one in \citet{Dominik13}.
%For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo\, is %fixed
\textbf{sampled from a uniform distribution} 
between $[M_{min}, m_1]$. Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF. 
\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}). We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system. We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.

Concerning the BHMF we consider two scenarios. In the first scenario, the exponent $\alpha$ is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET. In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
% \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably. Therefore the above ansatz is actually the first order Taylor expansion in the scale factor $a(t)$ applicable for any function.}

@@

\textbf{The quantities measurable from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform. 
\blue{Let us note that physical quantities inferred from the LIGO detections had asymmetric upper and lower uncertainty limits, hence they followed the  ${\it skewed}$  distributions. Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density used to simulate the measured value} is:
 \begin{equation} \label{equ_lognorm}
P(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
 \end{equation}
\blue{We set up the uncertainties for ${\cal M}_0$, \dl, and \mone\ by taking results of \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories. Note that the assumed uncertainty level of these quantities only affect the uncertainty of the inferred parameters (i.e. the precision) and wouldn't affect the validity test of our method (i.e. the  accuracy).
}

@@

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{{\bf Illustration of the mock GW catalog}} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $8.14\substack{+1.80\\-1.48}$  & $25356.8\substack{+5614.1\\-4596.4}$  & $9.91\substack{+2.19\\-1.80}$ & 18.512 \\
ID2 & $43.93\substack{+9.73\\-7.96}$  & $12956.9\substack{+2868.7\\-2348.7}$  & $28.64\substack{+6.34\\-5.19}$ & 46.953 \\
ID3 & $5.05\substack{+1.12\\-0.92}$  & $8617.6\substack{+1908.0\\-1562.1}$  & $3.60\substack{+0.80\\-0.65}$ & 9.836 \\
ID4 & $13.93\substack{+3.08\\-2.53}$  & $47473.1\substack{+10510.7\\-8605.4}$  & $10.97\substack{+2.43\\-1.99}$ & 17.563 \\
ID5 & $11.37\substack{+2.52\\-2.06}$  & $21485.0\substack{+4756.8\\-3894.6}$  & $10.68\substack{+2.36\\-1.94}$ & 31.107 \\
ID6 & $21.67\substack{+4.80\\-3.93}$  & $9446.1\substack{+2091.4\\-1712.3}$  & $7.64\substack{+1.69\\-1.39}$ & 31.624 \\
ID7 & $32.20\substack{+7.13\\-5.84}$  & $69317.4\substack{+15347.1\\-12565.1}$  & $19.35\substack{+4.28\\-3.51}$ & 13.496 \\
ID8 & $7.73\substack{+1.71\\-1.40}$  & $25104.5\substack{+5558.2\\-4550.7}$  & $6.68\substack{+1.48\\-1.21}$ & 9.612 \\
ID9 & $35.63\substack{+7.89\\-6.46}$  & $16321.8\substack{+3613.7\\-2958.6}$  & $10.96\substack{+2.43\\-1.99}$ & 16.202 \\
ID10 & $18.78\substack{+4.16\\-3.40}$  & $54375.1\substack{+12038.8\\-9856.5}$  & $15.16\substack{+3.36\\-2.75}$ & 29.232 \\
... & $...$ & ... & ... & ...\\
ID991 & $29.40\substack{+6.51\\-5.33}$  & $40765.1\substack{+9025.5\\-7389.5}$  & $29.79\substack{+6.59\\-5.40}$ & 28.134 \\
ID992 & $6.41\substack{+1.42\\-1.16}$  & $16026.7\substack{+3548.4\\-2905.2}$  & $4.54\substack{+1.01\\-0.82}$ & 17.550 \\
ID993 & $10.27\substack{+2.27\\-1.86}$  & $33207.9\substack{+7352.3\\-6019.6}$  & $8.57\substack{+1.90\\-1.55}$ & 8.037 \\
ID994 & $21.26\substack{+4.71\\-3.85}$  & $56088.6\substack{+12418.2\\-10167.1}$  & $16.01\substack{+3.54\\-2.90}$ & 19.871 \\
ID995 & $14.35\substack{+3.18\\-2.60}$  & $29022.0\substack{+6425.6\\-5260.8}$  & $13.50\substack{+2.99\\-2.45}$ & 14.230 \\
ID996 & $22.50\substack{+4.98\\-4.08}$  & $49038.7\substack{+10857.3\\-8889.2}$  & $18.48\substack{+4.09\\-3.35}$ & 11.636 \\
ID997 & $5.42\substack{+1.20\\-0.98}$  & $23537.5\substack{+5211.3\\-4266.6}$  & $4.54\substack{+1.01\\-0.82}$ & 12.562 \\
ID998 & $25.07\substack{+5.55\\-4.55}$  & $19555.4\substack{+4329.6\\-3544.8}$  & $18.81\substack{+4.16\\-3.41}$ & 17.846 \\
ID999 & $5.70\substack{+1.26\\-1.03}$  & $24024.9\substack{+5319.2\\-4355.0}$  & $3.61\substack{+0.80\\-0.65}$ & 23.020 \\
ID1000 & $39.23\substack{+8.69\\-7.11}$  & $31835.1\substack{+7048.4\\-5770.7}$  & $22.31\substack{+4.94\\-4.04}$ & 15.884 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET. The reported values are the medians, with errors corresponding to the 16th and 84th percentiles, {\bf assuming $\alpha=1.6$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$. Note that this mock data is re-simulated every time in each realization}.
}
\end{deluxetable}

@@

\subsection{Selection Effect}\label{sec_likelihood_sf}
The GW observations have a tendency to discover more significant events, known as Malmquist bias. \blue{For example, the} GW systems with higher values \mone\ \blue{tend to} produce stronger signals and thus have a higher probability to be detected. \blue{As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account}.

To overcome this selection effect, we introduce the selection factor $\eta$ for the GW event, which is the detecting probability of one event in a repeated simulation. 
The meaning of this factor $\eta$ is straightforward -- if one GW event has $\eta=0.2$, it means that this event has 80\% probability of being be missed. In other words, four equivalent events would have been missed. Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the intrinsic probability value. Hence, to account for the selection effect, we calculate the likelihood as:}
 \begin{equation} \label{equ_lik_sf}
 P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
 \end{equation}
where $\eta$ is directly determined by the probability distribution of $\rho$, i.e. $\eta = P(\rho>8)$. In order to \blue{use the Equation~(\ref{SNR}) to calculate $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}. Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors; one can only take the \dl\ as redshift estimator.
\blue{Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal). Thus, the distribution of their product $\eta$ is also asymmetric. Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}. Let us remind that in a Log-Normal distribution, the expected value is higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
We consider this skewness and recalibrate the inferred expected value of $1/\eta$ to the median value, in order to assign a non-biased $1/\eta$ to the calculation.
}

\begin{figure}%[!b]
\includegraphics[width=1.0\linewidth]{eta_distribution.pdf}
\caption{
\blue{
Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution. The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
}
}
\label{fig_eta}
\end{figure}

\subsection{Luminosity Distance as Redshift Estimator} 
\label{sec_dl_z}
%The redshift is not detectable by GW, however, can be inferred from the DL. 
In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$. The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function knowing the \dl$(z)$ and fixing the cosmological model.
